Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-07 ms.Rmd
Created final table for local adaptation

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt <- clubSandwich::conf_int(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
      robust_DispBgrdCC <- clubSandwich::coef_test(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")
      robust_DispBgrdCC_inter <- clubSandwich::coef_test(DispBgrdCC_inter, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

   # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
   robust_CourtshipAC <- clubSandwich::coef_test(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

@@

  # Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
  robust_CourtshipCC <- clubSandwich::coef_test(CourtshipCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

@@

@@

```{r table2, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

@@

>>>>

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt_DispBgrdAC <- clubSandwich::conf_int(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
      robust_DispBgrdCC <- clubSandwich::conf_int(DispBgrdCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

@@

   # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
   robust_CourtshipAC <- clubSandwich::conf_int(CourtshipAC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

@@

  # Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
  robust_CourtshipCC <- clubSandwich::conf_int(CourtshipCC, cluster = CourtshipBgrd$ID, vcov =  "CR2")

@@

# Social context. We only need models because contarsts are already there

@@

# Predators - Models AND contrasts. We don't get all contrasts because we have two factors in model
```{r table2, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

@@

# Local Adaptation. We have all the contrasts we need from the model because we are only comparing Hawaii-Hawaii(background) to Hawaii-Kenya(background). These are therefore in the table output already.

```{r table4, fig.width = 9, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Mean differences between Hawaiian lizards on introduced Hawaiian background and native Kenyan background."}

tb4 <- data.frame(rbind(robust_localAdapt_DispBgrdAC,
             robust_DispBgrdCC,
             robust_CourtshipAC,
             robust_CourtshipCC))
tb4$parameter <- rownames(tb4)
rownames(tb4) <- NULL

tb4 <- tb4 %>% mutate(SocialContext = c("Male-Male Display", rep("", 5), 
                                        "Courtship Display", rep("", 5)),
                    VisualRealm = c("Acromatic Contrast", rep("", 2), "Chromatic Contrast", 
                                    rep("", 2), "Acromatic Contrast", rep("", 2), 
                                    "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, parameter, beta, SE, df, CI_L, CI_U)

table4 <- flextable(tb4) %>% table_style9()
